---
title: "data-exploration"
author: "Inna Galat"
date: "8 July 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
ptStart <- proc.time()

library(data.table)
library(ggplot2)
library(corrplot)

projpath <- file.path("~","Github", "sales-prediction-r")
datapath <- file.path(projpath,"data")
```

## Preface

### 1. Reading Datasets

```{r datasets-reading}

train <- fread(file.path(datapath,"Train_UWu5bXk.txt"))
test <- fread(file.path(datapath,"Test_u94Q5KV.txt"))
names(train)
names(test)
summary(train)
head(train,4)

dplyr::count(unique(train[,1]))
lapply(train[,c(3,5,9,10,11)],unique)
dplyr::count(unique(train[,7]))
```

Item_Outlet_Sales column is a target variable, which is present only in train dataset. The rest of columns are dependent variables.

Item_identifier: 1556 unique values, character;
Item_weight: numerical variable, float;
Item_fat_content: at the moment shows 5 levels. After cleaning and fixing number of unique levels will drop;
Item_Visibility: ??percentage 
Item_type: 16 levels, may need some grouping by diff categories;
Item_MRP: numerical variable, float;
Outlet_identifier: character, has 10 unique levels;
Outlet_Establishment_Year: ordinal variable showing teh year;
Outlet_Size: 4 unique values, one of which is empty, will need to be transformed to nan;
Outlet_Location_Type: 3 unique values, may be ordinal of character;
Outlet_Type: 4 unique levels, character;




## Including Plots

You can also embed plots, for example:

```{r plot, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
